---
title: "World Bank Corpus Analysis"
author: "Huy Dang"
output:
  pdf_document:
    toc: yes
  html_document:
    number_sections: yes
    toc: yes
---
    
    ```{r, echo = T, message=FALSE}
    library("quanteda")
    library("tm")
    library("readtext")
    library("stringr")
    library("ggplot2")
    library("syllable")

    ```


```{r}
#Load data
path_data <- setwd("/Users/dangngochuy/Desktop/Hertie/Hertie\ 3rd\ semester/Natural\ Language\ Processing/World-Bank-Corpus-Analysis/Code")
wb_corpus_files <- readtext(paste0(path_data, "/OCR_Data/*"),
                    docvarsfrom = "filenames", 
                    dvsep = "_",
                    docvarnames = c("Organization", "Type", "Year"),
                    encoding = "ISO-8859-1")

wb_corpus_files$doc_id <- str_replace(wb_corpus_files$doc_id , ".txt", "") %>%
   str_replace(. , "_\\d{2}", "")

```

```{r}
#create corpus object

wb_corpus <- corpus(wb_corpus_files, text_field = "text") 

```

```{r}
# Inspect corpus to detect data issues
summary(wb_corpus)
```

PRE-PROCESS THE DATA:  

- Remove punctuation
- Remove digits
- Convert words to lower case? 

EXPLORATORY ANALYSIS: 

- Word cloud
- DMF

MEASURE READABILITY OF WORLD BANK CORPUR

```{r}
# Create readability measures for World Bank Corpus
wb_read <- textstat_readability(wb_corpus,
                     measure = c("Flesch", "Flesch.Kincaid", "FOG"))

```

FRE SCORES:

Flesch reading ease measures how complex a text is. The lower the score, the more difficult the text is to read. The Flesch readability score uses the average length of your sentences (measured by the number of words) and the average number of syllables per word in an equation to calculate the reading ease. Text with a very high Flesch reading ease score (about 100) is straightforward and easy to read, with short sentences and no words of more than two syllables. The lower the Flesch reading score is, the harder it is to peruse the text. 


```{r}
# Plot distribution of FRE scores over the years

plot(wb_read$Flesch, type = 'l', xaxt = 'n', xlab = "Flesch Reading Ease (FRE) Measure of World Bank Annual Reports", ylab = "Flesch Score")
grid()
axis(1, at = seq_len(nrow(wb_read)), labels = docvars(wb_corpus, 'Year'))

```


FLESCH KINCAID SCORE

Flesch-Kincaid Grade Level classifications are based on:
- Sentence length as judged by the average number of words in a sentence
- Word length as judged by the average number of syllables in a word.
The higher the score is, the more difficult the text is. 

```{r}
plot(wb_read$Flesch.Kincaid, type = 'l', xaxt = 'n', xlab = "Flesch Kincaid Measure of World Bank Annual Reports", ylab = "Flesch Kincaid Score")
grid()
axis(1, at = seq_len(nrow(wb_read)), labels = docvars(wb_corpus, 'Year'))
```

GUNNING FOG 

The Gunning Fog formula generates a grade level, typically between 0 and 20. The formula estimates the years of formal education the reader requires to understand the text on first reading.

The formula for Gunning Fog is 0.4 [(words/sentences) + 100 (complex words/words)], where complex words are defined as those containing three or more syllables.

- Score of 15-20 would indicate academic-level papers
- Score of over 20 denotes that this is a complex text

```{r}
plot(wb_read$FOG, type = 'l', xaxt = 'n', xlab = "Gunning Fog Measure of World Bank Annual Reports", ylab = "Gunning Fog Score")
grid()
axis(1, at = seq_len(nrow(wb_read)), labels = docvars(wb_corpus, 'Year'))

```

```{r}

#set up readability score functions

flesch_kincaid_ <- function(n.words, n.sents, n.sylls, ...){
    (.39*(n.words/n.sents)) + (11.8*(n.sylls/n.words)) - 15.9
}

gunning_fog_ <- function(n.words, n.sents, n.complexes, ...){
    .4*((n.words/n.sents) + (100*(n.complexes/n.words)))
}

coleman_liau_ <- function(n.words, n.sents, n.chars, ...) {
    (0.0588 * ((100 * n.chars)/n.words)) - (0.296 * ((100 * n.sents)/n.words)) - 15.8
}

smog_ <- function(n.sents, n.polys) {
    (1.043 * sqrt(n.polys * (30/n.sents))) + 3.1291
}


#automated_readability_index_  <- function(n.words, n.sents, n.chars){
#    4.71 * (n.chars/n.words) + 0.5 * (n.words/n.sents) - 21.43
#}

automated_readability_index_  <- function(n.words, n.sents, n.chars){
    out <- 4.71 * (n.chars/n.words) + 0.5 * (n.words/n.sents) - 21.43
    ceiling(ifelse(out < 1, 1, out)) - 1
}

SE <- function(x) sqrt(stats::var(x)/length(x))

digit_format <- function (x, digits = 1) {
    if (is.null(digits))
        digits <- 3
    if (length(digits) > 1) {
        digits <- digits[1]
        warning("Using only digits[1]")
    }
    x <- round(as.numeric(x), digits)
    if (digits > 0)
        x <- sprintf(paste0("%.", digits, "f"), x)
    out <- gsub("^0(?=\\.)|(?<=-)0", "", x, perl = TRUE)
    out[out == "NA"] <- NA
    out
}
```

```{r}

#' Grade Level Readability 
#' Calculate the Flesch Kincaid, Gunning Fog Index, Coleman Liau, SMOG,
#' Automated Readability Index and an average of the 5 readability scores.

readability <- function(x, grouping.var, order.by.readability = TRUE, group.names, ...){

    n.sents <- n.words <- n.complexes <- n.polys <- n.chars <- Flesch_Kincaid <-
        Gunning_Fog_Index <- Coleman_Liau <- SMOG <- Automated_Readability_Index <-
        Average_Grade_Level <- n.sylls <- NULL

    if(is.null(grouping.var)) {
        G <- "all"
        grouping <- rep("all", length(x))
    } else {

         if (isTRUE(grouping.var)) {
                G <- "id"
                grouping <- seq_along(x)
        } else {

            if (is.list(grouping.var) & length(grouping.var) > 1) {
                m <- unlist(as.character(substitute(grouping.var))[-1])
                G <- sapply(strsplit(m, "$", fixed=TRUE), function(x) {
                        x[length(x)]
                    }
                )
                grouping <- grouping.var
            } else {
                G <- as.character(substitute(grouping.var))
                G <- G[length(G)]
                grouping <- unlist(grouping.var)
            }
        }

    }

    if(!missing(group.names)) {
        G <- group.names
    }

    y <- syllable::readability_word_stats_by(x, grouping, group.names = G)

    grouping <- attributes(y)[["groups"]]

    out <- y[, list(
        Flesch_Kincaid = flesch_kincaid_(n.words, n.sents, n.sylls),
        Gunning_Fog_Index = gunning_fog_(n.words, n.sents, n.complexes),
        Coleman_Liau  =  coleman_liau_(n.words, n.sents, n.chars),
        SMOG  =  smog_(n.sents, n.polys),
        Automated_Readability_Index = automated_readability_index_(n.words, n.sents, n.chars)
    ), by = grouping][, list(
        Average_Grade_Level = mean(c(Flesch_Kincaid, Gunning_Fog_Index, Coleman_Liau, SMOG, Automated_Readability_Index), na.rm=TRUE)
    ), by = c(
        grouping, "Flesch_Kincaid", "Gunning_Fog_Index", "Coleman_Liau", "SMOG", "Automated_Readability_Index"
    )]

    if (isTRUE(order.by.readability)){
        data.table::setorder(out, -Average_Grade_Level)
    }

    class(out) <- unique(c("readability", class(out)))
    attributes(out)[["groups"]] <- grouping
    out

}

#' Plots a readability Object

plot.readability <- function(x, ...){

    Value <- NULL

    x[["grouping.var"]] <- apply(x[, attributes(x)[["groups"]], with = FALSE], 1, paste, collapse = ".")
    x[["grouping.var"]] <- factor(x[["grouping.var"]], levels = rev(x[["grouping.var"]]))
    x <- x[, attributes(x)[["groups"]]:=NULL]
    y <- tidyr::gather_(x, "Measure", "Value", c("Flesch_Kincaid", "Gunning_Fog_Index",
        "Coleman_Liau", "SMOG", "Automated_Readability_Index"))

    y[["Measure"]] <- gsub("_", " ", y[["Measure"]])
    data.table::setDT(y)

    center_dat <- y[, list(upper = mean(Value) + SE(Value), lower = mean(Value) - SE(Value),
        means = mean(Value)), keyby = "grouping.var"]

    nms <- gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", attributes(x)[["groups"]], perl=TRUE)

    xaxis <- floor(min(y[["Value"]])):ceiling(max(y[["Value"]]))

    ggplot2::ggplot(y, ggplot2::aes_string(y = "grouping.var")) +
        ggplot2::geom_vline(xintercept = mean(center_dat[["means"]]), size=.75, alpha = .25, linetype="dashed") +
       # ggplot2::geom_point(ggplot2::aes_string(color = "Measure", x = "Value"), size=1.4) +
        ggplot2::geom_point(ggplot2::aes_string(color = "Measure", x = "Value"), size=2, shape=1) +
        ggplot2::geom_errorbarh(data = center_dat, size=.75, alpha=.4,
            ggplot2::aes_string(x = "means", xmin="upper", xmax="lower"), height = .3) +
        ggplot2::geom_point(data = center_dat, ggplot2::aes_string(x = "means"), alpha = .5, shape=15, size=3) +
        ggplot2::geom_point(data = center_dat, ggplot2::aes_string(x = "means"), size=1) +
        ggplot2::scale_x_continuous(breaks = xaxis) +
        ggplot2::ylab(paste(nms, collapse = " & ")) +
        ggplot2::xlab("Grade Level") +
        ggplot2::theme_bw() +
        ggplot2::scale_color_discrete(name="Readability\nScore")

}


#' Prints a readability Object

print.readability <- function(x, digits = 1, ...){

    key_id <- NULL

    colord <-colnames(x)
    cols <- c("Flesch_Kincaid", "Gunning_Fog_Index", "Coleman_Liau",
       "SMOG", "Automated_Readability_Index", "Average_Grade_Level")

    x[["key_id"]] <- 1:nrow(x)
    y <- tidyr::gather_(x, "measure", "value", cols)

    y[["value"]] <- digit_format(y[["value"]], digits)
    y <- tidyr::spread_(y, "measure", "value")
    data.table::setDT(y)
    y <- y[order(key_id)]
    y[, "key_id"] <- NULL
    data.table::setcolorder(y, colord)
    print(y)
}
```

Plot readability scores

```{r}
wb_readability <- with(wb_corpus_files, readability(text, Year, order.by.readability = FALSE))
```

```{r}
plot(wb_readability)
```

```{r}
str(presidential_debates_2012)

```

```{r}
str(wb_corpus_files)
```

